Grow with the flow: faster growth is associated with more variable precipitation in a perennial herb

### 2016-10-12 ms/ms.Rnw
Worked on ms and figures

<<focClim, echo = FALSE, results=hide, warning=FALSE>>=
# Read in climate data for 16 focal populations to use in making Table 1
load(paste(pathDat, "/focClim.RData", sep = ""))

# Read in spatially-averaged (62 km buffer) for 16 focal populations
# *** still need to make this filer ***
load(paste(pathDat, "/focClimSA_62km.RData", sep = ""))

@@

@@

  # Figure of variable importance for latitude
  pdf(paste(pathFig, "/Figure_clim2lat_imp.pdf", sep = ""), 4, 5)
  par(mar = c(5, 6, 1, 1))
  plot(0, 0, type = "n", xlim = c(0, ceiling(vsurfLat$imp.mean.dec)[1]), 
		ylim = c(1, length(vsurfLat$varselect.pred)), axes = F, frame.plot = T, 
		xlab = "", ylab = "")
	title(xlab = "Climate-Latitude\nImportance", line = 4, cex.lab = 1.5)
  for (i in 1:length(vsurfLat$varselect.pred)) 
  {
     lines(x = c(-1, length(vsurfLat$varselect.pred)), y = c(i, i), 
           col = "grey")
  }
  points(vsurfLat$imp.mean.dec[1:length(vsurfLat$varselect.pred)], 
    length(vsurfLat$varselect.pred):1, pch = 21, col = "black", bg = "white",
    cex = 1.5)
	# mtext(climVars[vsurfLat$varselect.pred], side = 2, 
  #   at = length(vsurfLat$varselect.pred):1, las = 1, line = 1)
	axis(1, lwd = 0, lwd.ticks = 1)
	dev.off()

  # Variable selection using random forests (VSURF)
	# Climate variables that predict PC1 (point and spatially averaged)
  set.seed(69648)
  vsurfPC1 <- VSURF(focClim[, climVars], focClim[, "PC1"])
  vsurfPC1_SA <- VSURF(focClimSA[, climVars], focClimSA[, "PC1"])

##### WORKING ON STUFF HERE - can't finish until SA analysis with 62 km buffer finishes #####
# x <- match(vsurfPC1$imp.mean.dec.ind, vsurfPC1_SA$imp.mean.dec.ind)
# plot(vsurfPC1$imp.mean.dec, vsurfPC1_SA$imp.mean.dec[x], type = "n")
# text(vsurfPC1$imp.mean.dec, vsurfPC1_SA$imp.mean.dec[x], 
#		 labels = climVars[vsurfPC1$imp.mean.dec.ind])
# cor.test(vsurfPC1$imp.mean.dec, vsurfPC1_SA$imp.mean.dec[x])

@@

  # Overlap between latitude predictors and phenotype predictors (point measurements)
  imp2 <- climVars[vsurfPC1$varselect.pred]
  nImpPC1 <- length(imp2)

  # Figure of variable importance for traits (point measurements)
	pdf(paste(pathFig, "/Figure_clim2pc1_imp.pdf", sep = ""), 4, 5)
	par(mar = c(5, 1, 1, 6))

	plot(0, 0, type = "n", xlim = c(0, 0.2), ylim = c(1, nImpLat), 
		axes = F, frame.plot = T, xlab = "", ylab = "")
	title(xlab = "Climate-Trait PC1\nImportance", line = 4, cex.lab = 1.5)
	for (i in (nImpLat:(nImpLat - nImpPC1 + 1))) 
	{
		lines(x = c(-100, 100), y = c(i, i), col = "grey")
	}
	points(vsurfPC1$imp.mean.dec[1:nImpPC1], nImpLat:(nImpLat - nImpPC1 + 1), 
		pch = 21, col = "black", bg = "white", cex = 1.5)
	mtext(climVars[vsurfPC1$varselect.pred], side = 4, las = 1, line = 1, 
    at = nImpLat:(nImpLat - nImpPC1 + 1), 
		font = ifelse(vsurfPC1$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))
	axis(1, lwd = 0, lwd.ticks = 1, at = seq(0, 0.2, 0.05))
  dev.off()

  # Overlap between latitude predictors and phenotype predictors (spatial aveage)
  imp3 <- climVars[vsurfPC1_SA$varselect.pred]
  nImpPC1_SA <- length(imp3)

  # Figure of variable importance for traits (point measurements)
	pdf(paste(pathFig, "/Figure_clim2pc1SA_imp.pdf", sep = ""), 4, 5)
	par(mar = c(5, 1, 1, 6))

	plot(0, 0, type = "n", xlim = c(0, 0.3), ylim = c(1, nImpLat), 
		axes = F, frame.plot = T, xlab = "", ylab = "")
	title(xlab = "Climate-Trait PC1\nImportance", line = 4, cex.lab = 1.5)
	for (i in (nImpLat:(nImpLat - nImpPC1 + 1))) 
	{
		lines(x = c(-100, 100), y = c(i, i), col = "grey")
	}
	points(vsurfPC1$imp.mean.dec[1:nImpPC1], nImpLat:(nImpLat - nImpPC1 + 1), 
		pch = 21, col = "black", bg = "white", cex = 1.5)
	# mtext(climVars[vsurfPC1$varselect.pred], side = 4, las = 1, line = 1, 
  #  at = nImpLat:(nImpLat - nImpPC1 + 1), 
	#	font = ifelse(vsurfPC1$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))
	axis(1, lwd = 0, lwd.ticks = 1, at = seq(0, 0.3, 0.1))
  dev.off()

@@

clim2sym <- read.csv(paste(pathMS, "/climVar2plot.csv", sep = ""), 
										 stringsAsFactors = F, row.names = 1)
readLines(paste(pathMS, "/climVar2plot.csv", sep = ""))

@@

\subsection*{Remarkably little evidence for variation in plasticity}

>>>>

<<focClim, echo = FALSE, results=hide, warning=FALSE>>=

# Read in climate data for 16 focal populations to use in making Table 1
load(paste(pathDat, "/focClim.RData", sep = ""))

# Read in spatially-averaged (62 km buffer) for 16 focal populations
load(paste(pathDat, "/focClimSA_62km.RData", sep = ""))

@@

  # Variable selection using random forests (VSURF)
	# Climate variables that predict PC1 (point and spatially averaged)
  set.seed(69648)
  vsurfPC1 <- VSURF(focClim[, climVars], focClim[, "PC1"], parallel = TRUE,
                    ncores = 3, ntree = 1e4)
  climVars[vsurfPC1$varselect.pred]
  vsurfPC1_SA <- VSURF(focClimSA[, climVars], focClimSA[, "PC1"], 
                       parallel = TRUE, ncores = 3, ntree = 1e4)
  climVars[vsurfPC1_SA$varselect.pred]

  imp2 <- climVars[vsurfPC1$varselect.pred]
  nImpPC1 <- length(imp2)

  imp3 <- climVars[vsurfPC1_SA$varselect.pred]
  nImpPC1_SA <- length(imp3)

@@

	# Table of symbols for plotting climatic factor labels
	clim2sym <- read.csv(paste(pathMS, "/climVar2plot.csv", sep = ""), 
										   stringsAsFactors = F, row.names = 1)

  # Figure of variable importance for latitude

	# Calculatins for plot dimensions
	sw1a <- strwidth(s = clim2sym[imp1, "climFactor"], units = "inches")
	sw2a <- strwidth(s = clim2sym[imp1, "tempScale"], units = "inches")
	sw3a <- strwidth(s = parse(text = clim2sym[imp1, "what"]), units = "inches")

	sw1b <- strwidth(s = clim2sym[imp2, "climFactor"], units = "inches")
	sw2b <- strwidth(s = clim2sym[imp2, "tempScale"], units = "inches")
	sw3b <- strwidth(s = parse(text = clim2sym[imp2, "what"]), units = "inches")

	panelWidth <- 3
	panelHeight <- 4
	panelGap <- 0.1
	yLabWidth <- 4 * panelGap + sum(max(c(sw1a, sw1b)), max(c(sw2a, sw2b)),
	                                max(c(sw3a, sw3b)))
  xLabHeight <- 1

  pdf(paste(pathFig, "/Figure_ClimVarImp.pdf", sep = ""), 
      width = 2 * (yLabWidth + panelWidth) + panelGap, 
      height = panelHeight + xLabHeight + panelGap)
  par(mai = c(xLabHeight, yLabWidth, panelGap, panelGap / 2), mfrow = c(1, 2))

  # Panel A: Climate-Latitude
  plot(0, 0, type = "n", xlim = c(0, ceiling(vsurfLat$imp.mean.dec)[1]), 
		ylim = c(1, length(vsurfLat$varselect.pred)), axes = F, frame.plot = T, 
		xlab = "", ylab = "")
  abline(h = 1:nImpLat, col = "grey")
  points(vsurfLat$imp.mean.dec[1:length(vsurfLat$varselect.pred)], 
    length(vsurfLat$varselect.pred):1, pch = 21, col = "black", bg = "white",
    cex = 1.5)

  # X axis & labels
	axis(1, lwd = 0, lwd.ticks = 1)
  title(xlab = "Climate-Latitude\nImportance", line = 4, cex.lab = 1.5)

  # Y labels
	clip(grconvertX(0, from = "nfc", to = "user"), 
	     grconvertX(1, from = "nfc", to = "user"),
	     grconvertY(0, from = "nfc", to = "user"),
	     grconvertY(1, from = "nfc", to = "user"))

	text(grconvertX(panelGap / 2, from = "in", to = "user"), 
	     nImpLat:1, pos = 4, labels = clim2sym[imp1, "climFactor"])
  text(grconvertX(panelGap + max(c(sw1a, sw1b)), from = "in", to = "user"), 
       nImpLat:1, pos = 4, labels = clim2sym[imp1, "tempScale"])
	text(grconvertX(3 / 2 * panelGap + max(c(sw1a, sw1b)) + max(c(sw2a, sw2b)), 
	                               from = "in", to = "user"), nImpLat:1, pos = 4,
	                labels = parse(text = clim2sym[imp1, "what"]))

	# Panel B: Climate-PC1
	par(mai = c(xLabHeight, panelGap / 2, panelGap, yLabWidth))
	plot(0, 0, type = "n", xlim = c(0, 0.2), ylim = c(1, nImpLat), 
		axes = F, frame.plot = T, xlab = "", ylab = "")
	abline(h = nImpLat:(nImpLat - nImpPC1 + 1), col = "grey") 
	points(vsurfPC1$imp.mean.dec[1:nImpPC1], nImpLat:(nImpLat - nImpPC1 + 1), 
		pch = 21, col = "black", bg = "white", cex = 1.5)

	# X axis & labels
	axis(1, lwd = 0, lwd.ticks = 1, at = seq(0, 0.2, 0.05))
	title(xlab = "Climate-Trait PC1\nImportance", line = 4, cex.lab = 1.5)

  # Y labels
	clip(grconvertX(0, from = "nfc", to = "user"), 
	     grconvertX(1, from = "nfc", to = "user"),
	     grconvertY(0, from = "nfc", to = "user"),
	     grconvertY(1, from = "nfc", to = "user"))

	text(grconvertX(yLabWidth + 2 * panelWidth + 3 / 2 * panelGap, 
	                from = "in", to = "user"), 
	     nImpLat:(nImpLat - nImpPC1 + 1), pos = 4, 
	     labels = clim2sym[imp2, "climFactor"])
  text(grconvertX(yLabWidth + 2 * panelWidth + 5 / 2 * panelGap + 
                    max(c(sw1a, sw1b)), from = "in", to = "user"), 
       nImpLat:(nImpLat - nImpPC1 + 1), pos = 4, 
       labels = clim2sym[imp2, "tempScale"])
	text(grconvertX(yLabWidth + 2 * panelWidth + 5 / 2 * panelGap + 
                    max(c(sw1a, sw1b)) + max(c(sw2a, sw2b)), from = "in", 
	                to = "user"), nImpLat:(nImpLat - nImpPC1 + 1), pos = 4,
	                labels = parse(text = clim2sym[imp2, "what"]))

# x <- match(vsurfPC1$imp.mean.dec.ind, vsurfPC1_SA$imp.mean.dec.ind)
# plot(vsurfPC1$imp.mean.dec, vsurfPC1_SA$imp.mean.dec[x], type = "n")
# text(vsurfPC1$imp.mean.dec, vsurfPC1_SA$imp.mean.dec[x], 
#		 labels = climVars[vsurfPC1$imp.mean.dec.ind])
# cor.test(vsurfPC1$imp.mean.dec, vsurfPC1_SA$imp.mean.dec[x])

@@

  # Overlap between latitude predictors and phenotype predictors (spatial aveage)

  # Figure of variable importance for traits (spatially averaged)
	pdf(paste(pathFig, "/Figure_clim2pc1SA_imp.pdf", sep = ""), 4, 5)
	par(mar = c(5, 1, 1, 6))

	plot(0, 0, type = "n", xlim = c(0, 0.3), ylim = c(1, nImpLat), 
		axes = F, frame.plot = T, xlab = "", ylab = "")
	title(xlab = "Climate-Trait PC1\nImportance", line = 4, cex.lab = 1.5)
	for (i in (nImpLat:(nImpLat - nImpPC1_SA + 1))) 
	{
		lines(x = c(-100, 100), y = c(i, i), col = "grey")
	}
	points(vsurfPC1_SA$imp.mean.dec[1:nImpPC1_SA], 
	       nImpLat:(nImpLat - nImpPC1_SA + 1), 
	       pch = 21, col = "black", bg = "white", cex = 1.5)
	mtext(climVars[vsurfPC1_SA$varselect.pred], side = 4, las = 1, line = 1, 
    at = nImpLat:(nImpLat - nImpPC1_SA + 1), 
		font = ifelse(vsurfPC1_SA$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))
	axis(1, lwd = 0, lwd.ticks = 1, at = seq(0, 0.3, 0.1))
  dev.off()

@@

clim2sym <- read.csv(paste(pathMS, "/climVar2plot.csv", sep = ""), 
										 stringsAsFactors = F, row.names = 1)

@@

\subsection*{Little evidence for variation in plasticity}
